Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2022-07-19 write-up/fda-recurrent.tex
added figs to recreate at work comp

To address this, we use the recommendation from~\cite{Bartlett2020} and consider a method that first bootstraps a sample from the dataset and then apply multiple imputation to each bootstrap sample.  This general approach was originally proposed by~\cite{Shao1994} and~\cite{Little2002}. We suppose $B$ bootstraps and $M$ imputations per bootstrap; let $\hat \theta_{b,m}$ denote the estimator for the $m$th imputation of the $b$th bootstrap.  The point estimator is given by $(B)^{-1} \sum_{b=1}^B \hat \theta_{b}$ where $\hat \theta_b = M^{-1} \sum_{m=1}^M \hat \theta_{b,m}$. To construct the confidence interval, we require mean sum of squares with and between boostraps, i.e., $MSW = \frac{1}{B(M-1)} \sum_{b=1}^B \sum_{m=1}^M (\hat \theta_{b,m} - \hat \theta_b ) (\hat \theta_{b,m} - \hat \theta_b )^\top$ and $MSB = \frac{1}{B-1} \sum_{b=1}^B M \cdot (\hat \theta_b - \hat \theta)(\hat \theta_b - \hat \theta)^\top$ respectively. Then the estimator of the variance-covariance matrix of $\hat \theta$ is given by $\hat \Sigma_{B,M} = \left( \frac{B+1}{BM} \right) MSB - MSW/M$.  We obtain the varaiance for~$\beta(t)$ by $\phi (t) \hat \Sigma_{B,M} \phi(t)^\top$.  We follow~\cite{Bartlett2020} and construct confidence intervals based on Satterthwaite’s degrees of freedom, which here is given by
$$
\hat \nu = \phi (t) \hat \Sigma_{B,M} \phi(t)^\top
$$
The bootstrap followed by multiple imputation procedure has been studied extensively by~\cite{Bartlett2020} and is robust to uncongeniality.  The main disadvantage of this approach is its considerable computational intensity.  Recall likelihood calculations were computationally prohibitive by themselves, so combining with bootstrap and MI would further increase this large-scale computation.  The random subsampling framework thus simplifies handling of missing data via connections to function-on-scalar multiple imputation by~\cite{Petrovich2018} as well as to bootstrap to handle uncongeniality by~\cite{Bartlett2020}. Ignoring the computational time of bootstrap sampling, the computational time for the first choise in the simulation study with $B=200$ bootstraps and $M=2$ imputations per bootstrap leads to $35$ hours for a sampling rate of $0.5$ compared to $7$ hours for a sampling rate of $4$, which highlights the benefits of the proposed framework.

@@

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/eda_coef.png}
  \caption{Electrodermal activity (EDA)}
  \label{fig:eda_estimate}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/acc_coef.png}
  \caption{Activity Index (AI)
}  \label{fig:acc_estimate}
\end{subfigure}
\caption{$\beta (t)$ for ACC and EDA with 95\% CI; solid line is complete-case analysis, while dotted line is for }
\label{fig:mean_edacc}
\end{figure}

\subsection{Accounting for missing data and heterogeneity}

>>>>

To address this, we use the recommendation from~\cite{Bartlett2020} and consider a method that first bootstraps a sample from the dataset and then apply multiple imputation to each bootstrap sample.  This general approach was originally proposed by~\cite{Shao1994} and~\cite{Little2002}. We suppose $B$ bootstraps and $M$ imputations per bootstrap; let $\hat \theta_{b,m}$ denote the estimator for the $m$th imputation of the $b$th bootstrap.  The point estimator is given by $(B)^{-1} \sum_{b=1}^B \hat \theta_{b}$ where $\hat \theta_b = M^{-1} \sum_{m=1}^M \hat \theta_{b,m}$. To construct the confidence interval, we require mean sum of squares with and between boostraps, i.e., $MSW = \frac{1}{B(M-1)} \sum_{b=1}^B \sum_{m=1}^M (\hat \theta_{b,m} - \hat \theta_b ) (\hat \theta_{b,m} - \hat \theta_b )^\top$ and $MSB = \frac{1}{B-1} \sum_{b=1}^B M \cdot (\hat \theta_b - \hat \theta)(\hat \theta_b - \hat \theta)^\top$ respectively. Then the estimator of the variance-covariance matrix of $\hat \theta$ is given by $\hat \Sigma_{B,M} = \left( \frac{B+1}{BM} \right) MSB - MSW/M$.  We obtain the varaiance for~$\beta(t)$ by $\phi (t) \hat \Sigma_{B,M} \phi(t)^\top$.  We follow~\cite{Bartlett2020} and construct confidence intervals based on Satterthwaite’s degrees of freedom, which here is given by
$$
\hat \nu = \frac{\left[ \left( \frac{B+1}{BM} \right) MSB - \frac{MSW}{M} \right]^2}{ (B-1)^{-1} \left( \frac{B+1}{BM} \right)^2 MSB^2 + \frac{MSW^2}{BM^2(M-1)}}
$$
The bootstrap followed by multiple imputation procedure has been studied extensively by~\cite{Bartlett2020} and is robust to uncongeniality.  The main disadvantage of this approach is its considerable computational intensity.  Recall likelihood calculations were computationally prohibitive by themselves, so combining with bootstrap and MI would further increase this large-scale computation.  The random subsampling framework thus simplifies handling of missing data via connections to function-on-scalar multiple imputation by~\cite{Petrovich2018} as well as to bootstrap to handle uncongeniality by~\cite{Bartlett2020}. Ignoring the computational time of bootstrap sampling, the computational time for the first choise in the simulation study with $B=200$ bootstraps and $M=2$ imputations per bootstrap leads to $35$ hours for a sampling rate of $0.5$ compared to $7$ hours for a sampling rate of $4$, which highlights the benefits of the proposed framework.

@@

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/eda_coef_joint.png}
  \caption{Electrodermal activity (EDA)}
  \label{fig:eda_estimate}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/acc_coef_joint.png}
  \caption{Activity Index (AI)
}  \label{fig:acc_estimate}
\end{subfigure}
\caption{$\beta (t)$ for ACC and EDA with 95\% CI; solid line is complete-case analysis, while dotted line is for }
\label{fig:mean_edacc}
\end{figure}

\subsection{Accounting for missing data and heterogeneity}
\label{sec:missingdata_heterogeneity}
